H52F-05H: Robust Adaptation to\\Multi-Scale Climate Variability

### 2018-12-12 slides-agu/presentation.tex
update slides to be a bit less verbose

\begin{frame}{Idea 1: Risk Estimates over Finite Future Periods}
  \begin{alertblock}{Typical Approach:}
    \gls{cba}, probably with discounting, over a \alert{finite} planning horizon of $M$ years (explicitly or implicitly).
  \end{alertblock}
  \pause
  Project should be evaluated on climate conditions over this finite planning period:
  \begin{itemize}
    \item For ``mega-project'', $M \geq \SI{50}{years}$
    \item For small, flexible project, $M \leq \SI{5}{years}$
  \end{itemize}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How well can one identify and predict risk}
     associated with cyclical and secular climate signals over a finite planning period ($M$),  given limited information (\eg, an $N$-year record).
  \end{alertblock}
  \pause
  \begin{columns}
    \begin{column}{0.5\textwidth}
      In particular, we consider:
      \begin{itemize}
        \item the specific roles of $M$ and $N$;
        \pause
        \item estimation strategy (few processes/parameters $\Rightarrow$ many processes/parameters)
        \pause
        \item the form of the underlying climate signal.
      \end{itemize}
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{Example-NINO3-M100-N50-LN2.jpg}
        \caption{
          What is the bias and spread of $p(X > X^*)$?
          Here, $M=100$ and $N=50$.
          Subsequent results are tested systematically over $J=1000$ sequences.
        }
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Nonstationary Scenario II (Secular Change + LFV)}
  Conclusions are similar to ``Secular Change Only'' but variance has increased -- \ie as the system becomes more complex, more data is needed to understand it.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{lfv-secular-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

@@

\begin{frame}{Summary}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      Assertions:
      \begin{enumerate}
        \item Investment evaluation depends on climate condition over finite planning period
        \item Physical hydroclimate systems vary on many scales
        \item Physical drivers of risk depend on planning period
      \end{enumerate}    
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      Implications:
      \begin{itemize}
        \pause
        \item \emph{Ability} to identify and predict different climate signals depends on information available (\eg, $N$)
        \pause
        \item \emph{Importance} of identifying and predicting different climate signals depends on degree of extrapolation desired (\ie, $M$)
        \pause
        \item In general, low risk tolerance and/or short $N$ favor short-$M$ investments relative to long-$M$ ones.
      \end{itemize}    
    \end{column}
  \end{columns}
\end{frame}

>>>>

\begin{frame}{Idea 1: Risk Estimates over Finite Future Periods}
  \begin{alertblock}{Typical Approach:}
    \acrfull{cba}, probably with discounting, over a \alert{finite} planning horizon of $M$ years.
  \end{alertblock}
  \pause
  Project should be evaluated on climate conditions over this finite planning period:
  \begin{itemize}
    \item For ``mega-project'', $M \geq \SI{50}{years}$
    \item For small, flexible project, $M \leq \SI{5}{years}$
  \end{itemize}
\end{frame}

@@

\begin{frame}{Research Objective}
  \begin{alertblock}{How well can one identify and predict risk}
     associated with cyclical and secular climate signals over a finite planning period ($M$),  given limited information (\eg, an $N$-year record).
  \end{alertblock}
  \pause
  \begin{columns}
    \begin{column}{0.5\textwidth}
      In particular, we consider:
      \begin{itemize}
        \item the specific roles of $M$ and $N$;
        \pause
        \item estimation strategy (few processes/parameters $\Rightarrow$ many processes/parameters)
        \pause
        \item the form of the underlying climate signal.
      \end{itemize}
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      \begin{figure}
        \includegraphics[width=\textwidth]{Example-NINO3-M100-N50-Stationary-Trend.pdf}
        \caption{
          What is the bias and spread of $p(X > X^*)$?
          Here, $M=100$ and $N=50$.
          Subsequent results are tested systematically over $J=1000$ sequences.
        }
      \end{figure}
    \end{column}
  \end{columns}
\end{frame}

@@

\begin{frame}{Nonstationary Scenario II (Secular Change + LFV)}
  As the system becomes more complex, more data is needed to understand it.
  \begin{figure}
    \centering
    \includegraphics[width=\textwidth,height=0.625\textheight,keepaspectratio=true]{lfv-secular-nino3-bias-variance.pdf}
  \end{figure}
\end{frame}

@@

\begin{frame}{Summary}
  \begin{columns}[T]
    \begin{column}{0.5\textwidth}
      Assertions:
      \begin{itemize}
        \item Investment evaluation depends on climate condition over finite planning period
        \item Physical hydroclimate systems vary on many scales
        \item Physical drivers of risk depend on planning period
      \end{itemize}    
    \end{column}
    \pause
    \begin{column}{0.5\textwidth}
      Implications:
      \begin{itemize}
        \pause
        \item \emph{Ability} to identify and predict different climate signals depends on information available (\eg, $N$)
        \pause
        \item \emph{Importance} of identifying and predicting different climate signals depends on degree of extrapolation desired (\ie, $M$)
        \pause
        \item In general, low risk tolerance and/or short $N$ favor short-$M$ investments relative to long-$M$ ones.
      \end{itemize}    
    \end{column}
  \end{columns}
\end{frame}
